Paper Wireframe

### 2018-07-26 paper_wireframe_knit.Rmd
Shuffle env data read in to top and add new leaflet map

@@

@@

Compare this to when cuckoos leave their last stopover in central Africa

dat3<- env %>% group_by(year, ptt, SO_startDOY, variable) %>%
  summarise(country=last(country), SO_endDOY=first(SO_endDOY),
            cuck_pres=first(cuck_pres), precip=mean(value, na.rm=T),
            NDVI= mean(value2, na.rm=T), aquaNDVI=mean(aquaNDVI, na.rm=T),
            aquaANOM=mean(aquaANOM, na.rm=T),terrNDVI=mean(terrNDVI, na.rm=T), terrANOM=mean(terrANOM, na.rm=T), tamRAIN=mean(tamRAIN, na.rm=T), tamRAINanom=mean(tamRAINanom, na.rm=T) )

dat3[which(dat3$precip>500),]$precip<-0 # remove erroneous vals
dat3[which(is.na(dat3$precip)),]$precip<-0 # fix na

dat3<-dat3 %>% group_by(year, ptt, SO_startDOY) %>% dplyr::mutate(cumrf=cumsum(precip))

dat3<- dat3[which(dat3$country %in% c('Angola', 'Central African Republic','Congo', 'Democratic Republic of the Congo', 'Gabon',  'Cameroon')),]

temp<-dat3[dat3$cuck_pres=='Y',] %>% group_by(ptt, year) %>% summarise_all(last) %>% group_by(country) %>% summarise(MSO_endDOY=mean(SO_endDOY), Mrf=mean(cumrf), Mnd=mean(aquaNDVI, na.rm=T))

temp2<-dat3 %>% group_by(country, variable) %>% summarise(Mcumrf=mean(cumrf), rfmin=mean(cumrf)-sd(cumrf), rfmax=mean(cumrf)+sd(cumrf),                                                          MaquaNDVI=mean(aquaNDVI, na.rm=T), ndmin=(mean(aquaNDVI, na.rm=T)-sd(aquaNDVI, na.rm=T)), ndmax=(mean(aquaNDVI, na.rm=T)+sd(aquaNDVI, na.rm=T)))

p1<-ggplot()+
geom_line(data=temp2,aes(x=variable, y=Mcumrf), size=1, colour='blue')+
geom_line(data=temp2,aes(x=variable, y=rfmin), colour='grey', linetype=2)+
geom_line(data=temp2,aes(x=variable, y=rfmax), colour='grey', linetype=2)+  
geom_vline(data=(dat3[dat3$cuck_pres=='Y',] %>% group_by(ptt, year) %>% summarise_all(last)), aes(xintercept = SO_endDOY), colour='black', alpha=0.5)+
geom_vline(data=temp, aes(xintercept = MSO_endDOY), colour='red', size=1.5)+
   facet_grid(country~.)+xlab("Day of year")+
  ylab("Cumulative rainfall (mm)")+theme_bw()

p2<-ggplot()+geom_line(data=temp2,aes(x=variable, y=MaquaNDVI), size=1, colour='dark green')+
geom_line(data=temp2,aes(x=variable, y=ndmin), colour='orange', linetype=2)+
geom_line(data=temp2,aes(x=variable, y=ndmax), colour='orange', linetype=2)+
geom_vline(data=(dat3[dat3$cuck_pres=='Y',] %>% group_by(ptt, year) %>% summarise_all(last)), aes(xintercept = SO_endDOY), colour='black', alpha=0.5)+
geom_vline(data=temp, aes(xintercept = MSO_endDOY), colour='red', size=1.5)+
   facet_grid(country~.)+xlab("Day of year")+
  ylab("NDVI")+theme_bw()

>>>>

#### AND THE ENV DATA #####

@@

So what do these early leaving birds do in their runup to departing Cote d'Ivoire that is different to other birds?

soversWA1<-left_join(soversWA, dat[,c(1,2,6)], by=c('ptt', 'year'))

soversWA2<-left_join(soversWA1, dat2.2[,c(1,2, 3,7)], by=c('ptt', 'year', 'SO_startDOY'))

forsp<-na.omit(soversWA2[,c(1,2,7,8,9,17,18,22,23)])

forsp<-forsp %>% group_by(ptt, year) %>% mutate(nzz=n()) %>% filter(nzz>1) # drops Peckham in 2016 that cocks up linestring

dat_sp<-st_as_sf(forsp, coords = c("SO_median_long","SO_median_lat"), crs="+proj=longlat +datum=WGS84")

dat_ls<-dat_sp %>% group_by(ptt, year, DEPwestAF) %>% summarise(do_union=F) %>% st_cast("LINESTRING")

dat_ls

d2<-dat_sp[dat_sp$DEPwestAF<101,]
d3<-dat_sp[dat_sp$DEPwestAF>100,]

m <- leaflet() %>%
  addTiles() %>%

  addPolylines(data=dat_ls[dat_ls$DEPwestAF<101,], weight=1, color='blue', group='Early departure') %>%

    addPolylines(data=dat_ls[dat_ls$DEPwestAF>100,], weight=1, color='orange', group='Late departure') %>%

  addCircleMarkers(data=d2, popup= paste("ptt:", d2$ptt, "<br>", "year:", d2$year,"<br>", "NDVIanom:", d2$aquaANOM), color=~ifelse(aquaANOM>0, 'green', 'red'), stroke=F, radius=5, group='Early departure') %>%

    addCircleMarkers(data=d3, popup= paste("ptt:", d3$ptt, "<br>", "year:", d3$year,"<br>", "NDVIanom:", d3$aquaANOM), color=~ifelse(aquaANOM>0, 'green', 'red'), stroke=F, radius=5, group='Late departure') %>%

  addLayersControl(overlayGroups = c('Early departure', 'Late departure'), options=layersControlOptions(collapsed=F))

@@
